\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Giesecke + Devrient}{Jun 2023 -- Aug 2023}
      {Front End Dev Intern $|$ C\#, Blazor, Javascript, Bootstrap 5, Git}{Gurugram}
      \resumeItemListStart
        \resumeItem{Using C\# and Blazor, developed a tool to analyze the memory consumption of machines in use by banks, complete with interactive Plotly charts.}
        \resumeItem{Utilized Figma to design software screens and menu icons, ensuring a polished user interface.}
        \resumeItem{Leveraged Blazor, SCSS, and JavaScript to enhance user experience through seamless animations.}
        \resumeItem{Contributed to the optimization of design and code (more than 10+ screens), resulting in improved performance and responsive screens.}
      \resumeItemListEnd

    \resumeSubheading
      {MUJ NMS}{Mar 2024 -- April 2024}
      {Lead Front End Developer $|$ React.Js, Tailwind, Figma, Git, Node.js}{Remote}
      \resumeItemListStart
        \resumeItem{Utilizing React, created a portal for notesheet management, wherein faculty members of our college can add, edit, revert a notesheet. It also consists of timeline where users can see where the notesheet is currently at, and the status notesheet}
        \resumeItem{Created a private channel, where users can send messages to any other user to get their comments on the particular notesheet.}
        \resumeItem{Contributed in enhancing the UI/UX to create an intuitive interface and seamless navigation experience for new users.}
        \resumeItem{Employed best practices in web development (caching, context management, etc:-) to ensure optimal performance and accessibility.}
    \resumeItemListEnd

    \resumeSubheading
      {Philips}{Jul 2024 -- Present}
      {DevOps Intern $|$ Bash, Powershell, Python, Typescript, C\#, Github Actions, Git}{Bangalore}
      \resumeItemListStart
        \resumeItem{Built a CLI-based synchronization tool to replicate bugs between server instances, eliminating manual replication.}
        \resumeItem{Extended an open-source {\underline{\href{https://github.com/upptime/upptime}{uptime monitor}}} to develop a directory health monitor that provided real-time status pages and alerts for directories that are full, empty, etc.}
        \resumeItem{Automated SBOM uploads to Cybeats, streamlining vulnerability monitoring and management processes in production.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-10pt}
